Seminar paper on Probabilistic Near-Duplicate Detection Using Simhash

### 2019-07-08 ii/paper/paper.tex
STUFF

@@

W

>>>>

\newtheorem{lemma1}{Lemma}

@@

For defining such a data structure, a specific property of the Sets of considered bits must be ensured.

\begin{lemma1}
If two sets $S_1, S_2$ of the same size $h$ differ in exactly 1 bit and $S_1 \prec S_2$, then $∀u : p(u, S_1) \geq p(u, S_2)$.
\end{lemma1}

$\prec$ represents the lexicographical comparison operator on ${S}$. Lemma 1 describes that two sets $S_1 \prec S_2$, if there exists an index $i < h$ such that both sets have the same leading elements of length $i$, but $S_2$ is still larger in the $(i+1)$th element.

\begin{figure}[H]
\includegraphics[scale=0.4]{./gfx/vosh_algorithm.png}
\centering
\caption{Pseudocode representation for the generation of a Volatility Ordered Set Heap (VOSH).}\label{fig:weight-distribution}
\end{figure}

\begin{figure}[H]
\includegraphics[scale=0.4]{./gfx/vosh_structure.png}
\centering
\caption{Example for a generated VOSH structure generated by Algorithm 2.}\label{fig:weight-distribution}
\end{figure}
